### 2023-12-20 sections/4-results.tex
updated lfd plots

\begin{figure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/fashion-mnist-60000-lfd.png}\\
\subcaption{Fashion-mnist}
\label{fig:results:fashion-mnist-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/glove-25-1183514-lfd.png}\\
\subcaption{Glove-25}
\label{fig:results:glove-25-lfd}
\end{subfigure}
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/sift-1000000-lfd.png}\\
\subcaption{Sift}
\label{fig:results:sift-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/random-1000000-128-1000000-lfd.png}\\
\subcaption{A random dataset}
\label{fig:results:random-lfd}
\end{subfigure}
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/silva-2224640-lfd.png}\\
\subcaption{Silva 18S metagenomics}
\label{fig:results:silva-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/radioml-97920-lfd.png}\\
\subcaption{RadioML}
\label{fig:results:radioml-lfd}
\end{subfigure}%

@@

\begin{figure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
\subcaption{Fashion-mnist for $k=10$.}
\label{fig:results:fashion-mnist-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
\subcaption{Glove-25 for $k=10$.  }
\label{fig:results:glove-25-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
\subcaption{Sift for $k=10$.    }
\label{fig:results:sift-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/random-1000000-128-knn-10.png}
\subcaption{A random dataset for $k=10$.
}
\label{fig:results:random-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
\subcaption{Silva for $k=10$.    }
\label{fig:results:silva-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/radioml-knn-10.png}
\subcaption{RadioML for $k=10$.
}
\label{fig:results:radioml-scaling}
\end{subfigure}%

>>>>

\begin{figure}
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/fashion-mnist-60000-lfd.png}\\
\subcaption{Fashion-mnist}
\label{fig:results:fashion-mnist-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/glove-25-1183514-lfd.png}\\
\subcaption{Glove-25}
\label{fig:results:glove-25-lfd}
\end{subfigure}
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/sift-1000000-lfd.png}\\
\subcaption{Sift}
\label{fig:results:sift-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/random-1000000-lfd.png}\\
\subcaption{A random dataset}
\label{fig:results:random-lfd}
\end{subfigure}
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/silva-2224640-lfd.png}\\
\subcaption{Silva 18S metagenomics}
\label{fig:results:silva-lfd}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{images/lfd_plots/radio-ml-97920-lfd.png}\\
\subcaption{RadioML}
\label{fig:results:radioml-lfd}
\end{subfigure}%

@@

\begin{figure}
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
\subcaption{Fashion-mnist for $k=10$.}
\label{fig:results:fashion-mnist-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
\subcaption{Glove-25 for $k=10$.  }
\label{fig:results:glove-25-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
\subcaption{Sift for $k=10$.    }
\label{fig:results:sift-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/random-1000000-128-knn-10.png}
\subcaption{A random dataset for $k=10$.
}
\label{fig:results:random-scaling}
\end{subfigure}%
\vspace{1em}
\\
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
\subcaption{Silva for $k=10$.    }
\label{fig:results:silva-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.47\textwidth}
\includegraphics[width=0.95\textwidth]{plots/radioml-knn-10.png}
\subcaption{RadioML for $k=10$.
}
\label{fig:results:radioml-scaling}
\end{subfigure}%
